A publishing infrastructure for AI-assisted academic authoring

### 2024-03-26 latex/manuscript.tex
methods, results and latex: move text to supplementary material

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=1in,left=0.5in,right=0.5in,bottom=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
\usepackage[inkscapeformat=pdf,inkscapelatex=false,inkscapearea=page,inkscapepath=svgsubdir]{svg}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{american}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\usepackage[misc]{ifsym}

@@

We used the \href{https://openai.com/api/}{OpenAI API} for access to these models.
Since this API incurs a cost with each run that depends on the manuscript length, we implemented a workflow in GitHub Actions that can be manually triggered by the user.
Our implementation allows users to tune the costs to their needs by enabling them to select specific sections for revision instead of the entire manuscript.
Additionally, several model parameters can be adjusted to further tune costs, such as the language model version (including the current GPT-3.5 Turbo and GPT-4, and potentially newly published ones), how much risk the model will take, or the ``quality'' of the completions.
For instance, using Davinci models, the cost per run is under \$0.50 for most manuscripts.

@@

Assessing the performance of text generation tasks is challenging, and this is especially true for automatic revisions of scientific content.
In this context, we need to make sure the revision does not change the original meaning or introduce incorrect or misleading information.
For this reason, our approach emphasizes human assessments of the revisions to mitigate these issues, and we followed the same procedure in evaluating our tool.
We used three manuscripts of our own authorship (CCC, PhenoPLIER, and Manubot-AI; see below), which allowed us to assess changes in the original meaning and whether revisions retained important details.
During the prompt engineering phase (see below), we also used a unit testing framework to ensure that the revisions produced by our prompts met a minimum set of quality measures.
Finally, by incorporating two external manuscripts (BioChatter and Epistasis), we used the LLM-as-a-Judge technique {[}\protect\hyperlink{ref-LhEwBH2w}{14}{]}, where we asked an LLM to evaluate the quality of the revisions produced by another LLM.

\paragraph{Language models}

@@

\paragraph{Prompt engineering}

@@

However, other paragraphs in CCC required extensive changes before they could be incorporated into the manuscript.
For instance, the model generated revised text for certain paragraphs that was more concise, direct, and clear.
However, this often resulted in the removal of important details and occasionally altered the intended meaning of sentences.
To address this issue, we could accept the simplified sentence structure proposed by the model, but reintroduce the missing details for clarity and completeness.

@@

When revising the Methods sections of Manubot-AI (this manuscript), the model, in some cases, added novel sentences containing incorrect information.
For example, for one paragraph, it included a formula (using the correct Manubot format) presumably to predict the cost of a revision run.
In another paragraph (Supplementary Figure 2), it introduced new sentences stating that the model was \emph{``trained on a corpus of scientific papers from the same field as the manuscript''} and that its suggested revisions resulted in a \emph{``modified version of the manuscript that is ready for submission''}.
Although these are important future directions, neither statement accurately describes the present work.

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[top=1in,left=0.5in,right=0.5in,bottom=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
\usepackage[inkscapeformat=pdf,inkscapelatex=false,inkscapearea=page,inkscapepath=svgsubdir]{svg}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includesvg[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\usepackage[normalem]{ulem}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{american}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\usepackage[misc]{ifsym}

@@

We used the \href{https://openai.com/api/}{OpenAI API} for access to these models.
Since this API incurs a cost with each run that depends on the manuscript length, we implemented a workflow in GitHub Actions that can be manually triggered by the user.
Our implementation allows users to tune the costs to their needs by enabling them to select specific sections for revision instead of the entire manuscript.
Additionally, several model parameters can be adjusted to further tune costs, such as the language model version (including the current GPT-3.5 Turbo and GPT-4, and potentially newly published ones), how much risk the model will take, or the ``quality'' of the completions.
For instance, using Davinci models, the cost per run is under \$0.50 for most manuscripts.
More details about the implementation, installation, and usage of the Manubot AI Editor can be found in the \protect\hyperlink{sec:supp_mat}{Supplementary Material}.

@@

We used five different manuscript for the evaluation of our AI-based revision workflow (see below), and during the prompt engineering phase (see below), we also used a unit testing framework to ensure that the revisions produced by our prompts met a minimum set of quality measures (see Supplementary Material).

@@

@@

However, other paragraphs in CCC required extensive changes before they could be incorporated into the manuscript.
For instance, the model generated revised text for certain paragraphs that was more concise, direct, and clear.
However, this often resulted in the removal of important details and occasionally altered the intended meaning of sentences.
To address this issue, we could accept the simplified sentence structure proposed by the model but reintroduce the missing details for clarity and completeness.

@@

When revising the Methods sections of Manubot-AI (this manuscript), the model, in some cases, added novel sentences containing incorrect information.
For example, for one paragraph, it included a formula (using the correct Manubot format) presumably to predict the cost of a revision run.
In another paragraph (Supplementary Figure 2), it introduced new sentences stating that the model was \emph{``trained on a corpus of scientific papers from the same field as the manuscript''} and that its suggested revisions resulted in a \emph{``modified version of the manuscript that is ready for submission.''}
Although these are important future directions, neither statement accurately describes the present work.

@@

\clearpage
\setcounter{page}{1}
\subsection{Supplementary Material}

\subsubsection{Prompt engineering}
